---
title: "04-analysis"
output: pdf_document
---
#Analysis

```{r}
library(xtable)
library(readr)
library(Matrix)
options(xtable.floating = FALSE)
load('../../data/ols.RData')
load('../../data/ridge.RData')
load('../../data/lasso.RData')
load('../../data/pcr.RData')
load('../../data/plsr.RData')
```

## OLS
```{r,echo=FALSE,results='asis'}
olsTable <- xtable(olsSum$coefficients)
print(olsTable, comment=FALSE, type = "latex")
# OLS MSE
olsMSE
```

The ordinary least squares regression MSE is 0.044683. 

## Ridge 

```{r,echo=FALSE,results='asis'}
ridgeTable = as.matrix(ridgeFitcoef)
print(xtable(ridgeTable), comment = FALSE,type = 'latex')
ridgeMSE
```

The ridge regression MSE is 0.0525927.
When comparing the ridge regression with OLS, the results are similar.

## Lasso 

```{r,echo=FALSE,results='asis'}
lassoTable = as.matrix(LassoFitcoef)
print(xtable(ridgeTable), comment = FALSE,type = 'latex')
lassoMSE
```

The lasso regression MSE is 0.05154446
The lasso regression and ridge regression have the same results.

## Principal Components Regression

```{r,echo=FALSE,results='asis'}
pcrTable = as.matrix(pcrFitCoef)
print(xtable(pcrTable), comment = FALSE,type = 'latex')
pcrMSE
```

The PCR MSE is 0.05199678.
The PCR coefficients and OLS coefficients are similar. They also shared the similar results with ridge regression. 

## Partial Least Squares Regression

```{r,echo=FALSE,results='asis'}
plsrTable = as.matrix(plsrFitCoef)
print(xtable(plsrTable), comment = FALSE,type = 'latex')
plsrMSE
```

The PLSR MSE is 0.0517916.
The PLSR coefficients have some difference from PCR. When comparing with second and third components, PCR and PLSR have different results. The majority others remains the same. 
